A generic and fast C++ optimization framework

### 2017-10-19 paper.tex
Function type details

\noindent where {\tt arma::mat} is Armadillo's dense matrix type and {\tt
GaussianKernel} is a class that provides one simple {\tt Evaluate()} function
that returns the kernel value between its two arguments.  Since the {\tt
KernelType} argument is a template argument, any class can be used---it does not
need to be functionality supplied with mlpack.  Therefore, a user can simply
implement their own {\tt KernelType} class with the single {\tt Evaluate()}
function and use that as a template argument to the {\tt MeanShift} class, and
the compiler will generate a specialized implementation using the custom kernel.
Similar support could be accomplished by, e.g., function pointers (and this is
often done in other languages); however, templates allow us to avoid the runtime
cost of dereferencing the function pointer by generating code that directly
calls the correct function, which can be a non-negligible cost especially when
the function is called many times.

@@

@@

The framework provided by {\bf mlpack} supports a wide array of special cases,
and offers specialized algorithms that outperform their classic generic
alternatives.

>>>>

\noindent where {\tt arma::mat} is Armadillo's dense matrix type and {\tt
GaussianKernel} is a class that provides one simple {\tt Evaluate()} function
that returns the kernel value between its two arguments.  Since the {\tt
KernelType} argument is a template argument, any class can be used---it does not
need to be functionality supplied with mlpack.  Therefore, a user can simply
implement their own {\tt KernelType} class with the single {\tt Evaluate()}
function and use that as a template argument to the {\tt MeanShift} class, and
the compiler will generate a specialized implementation using the custom kernel.
Similar support could be accomplished by, e.g., function pointers (and this is
often done in other languages); however, templates allow us to avoid the runtime
cost of dereferencing the function pointer by generating code that directly
calls the correct function. This cost can be non-negligible, especially in
situations where the function is called many times, such as the {\tt Evaluate()}
function of an optimization problem.

@@

At the time of writing, we offer a few implementations of this API, each
designed to cover a special case.

\begin{itemize}
  \item{\tt FunctionType}: Requires the implementation of {\tt Evaluate()} and
  {\tt Gradient()}. This is a generic function that is used by the
  {\tt GradientDescent} optimizer.
  \item{\tt DecomposableFunctionType}: In addition to {\tt FunctionType}'s
  requirements, requires the implementation of {NumFunctions()}, which returns
  the number of parts the optimization problem can be decomposed into. The other
  two functions ({\tt Gradient(), Evaluate()}) accept an index as argument and
  only evaluate one of the decomposable parts. This is used by our {\tt AdaGrad}
  implementations, some {\tt SGD} implementations, {\tt RMSProp} and
  {\tt SMORMS3}.
  \item{\tt SparseFunctionType}: Similar to {\tt DecomposableFunctionType},
  however this function type returns a sparse gradient, which makes it ideal for
  sparse, parallelizable optimization problems. This function type is used by
  {\bf mlpack}'s parallel implementation of SGD, {\tt ParallelSGD}.
  \item{\tt LagrangianFunctionType}: This function type fits constrained
  optimization problems. It requires the implementation of {\tt NumConstraints},
  {\tt EvaluateConstraint()} and {\tt GradientConstraint}, which are required by
  optimizers like {\tt AugLagrangian} and {\tt LRSDP}.
\end{itemize}

In addition to these function types, certain optimizers require specific
functionality to achieve their goal. The {\tt FunctionType} API offers users the
flexibility to define a custom function signature. As an example, {\bf mlpack}'s
implementation of L-BFGS requires a function that exposes a
{\tt GetInitialPoint} function.

@@

The framework provided by {\bf mlpack} supports a wide array of special cases,
and offers specialized algorithms that outperform their classic generic
 (alternatives.
